Measuring Hash Trustworthiness via Collision Utility Metrics: Logical Cryptanalysis of MD4

### 2017-12-03 dsn-2018/bare_conf.tex
Minor word changes
Signed-off-by: Alexander Scheel <alexander.m.scheel@gmail.com>

We introduce a distance function, $\delta$ between collision classes by the
number of differences in intermediate rounds deltas. That is, given two
collision classes, $C_1, C_2 \in \mathcal{C}$:
\begin{align}
    \delta(C_1, C_2) = \big| \{ i : C_1[i] \neq C_2[i] \} \big|
\end{align}

@@

We define the neighborhood of a collision class, $C \in \mathcal{C}$, to be the
set of all other collisions at a fixed distance, $d \in \mathbb{N}$, from $C$.
That is:
\begin{align}
    N(C, d) & = \{ C_j \in \mathcal{C} : \delta(C, C_j) = d \} \\
    N(C) & = N(C, 1)
\end{align}
For instance, $C_{Wang} \in N(C_{Sasaki}, 21)$. The distance parameter, $d$,
may optionally be omitted, in which case the unit distance is implied. Thus,
$C_{Kasselman} \in N(C_{Dobbertin})$.

@@

We seek to build new intuition about collisions in hash functions,
specifically, collisions in MD4. By developing techniques from logical
cryptanalysis, we seek to complement and extend the results from
differential cryptanalysis. In particular, we wish to use logical cryptanalysis
to discuss the impacts of collisions in real-world systems. In this paper,
we introduce and give justification for general techniques, and present some
results of these techniques.

@@

The following techniques have been extensively tested on MD4 and partially
tested on MD5 and believe to apply fully to MD5. They may or may not apply
to any later hash function, such as SHA-1, SHA-2, or SHA-3, and have not been
tested yet.

In the following sections, we use the collisions of X. Wang \cite{Wang2005},
Y. Sasaki \cite{Sasaki2007}, M. Schl{\"a}ffer \cite{Schlaffer2006}, H. Dobbertin
\cite{Dobbertin1998}, and P. Kasselman \cite{KasselmanMD4} for examples.

>>>>

We introduce a distance function, $\delta$, between collision classes by the
number of differences in intermediate rounds deltas. That is, given two
collision classes, $C_1, C_2 \in \mathcal{C}$:
\begin{align}
    \delta(C_1, C_2) = \big| \{ i : C_1[i] \neq C_2[i] \} \big|
\end{align}

@@

We define the neighborhood of a collision class, $C \in \mathcal{C}$, to be the
set of all other non-empty collision classes at a fixed distance,
$d \in \mathbb{N}$, from $C$. That is:
\begin{align}
    N(C, d) & = \{ C_j \in \mathcal{C} : \delta(C, C_j) = d \} \\
    N(C) & = N(C, 1)
\end{align}
For instance, $C_{Wang} \in N(C_{Sasaki}, 21)$. The distance parameter, $d$,
may optionally be omitted, in which case the unit distance is implied. Thus,
$C_{Kasselman} \in N(C_{Dobbertin})$.

@@

We seek to build new intuition about collisions in hash functions
and particularly collisions in MD4. By developing techniques using logical
cryptanalysis, we seek to complement and extend the results from
differential cryptanalysis. In particular, we wish to use logical cryptanalysis
to discuss the impacts of collisions in real-world systems. In this paper,
we introduce and give justification for general techniques, and present some
results of these techniques.

@@

The following techniques have been extensively tested on MD4 and partially
tested on MD5 and believe to apply fully to MD5. They likely apply to any
hash function with similar structure, but as of yet, are untested.
